---
title: "Cyclistic Case Study"
author: "Steve Tamayo"
date: "2023-09-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is a report for the Case Study 1 of the Coursera Google Data Analytics Capstone.

## Business Task Statement

#### "How do annual members and casual riders use Cyclistic bikes differently?"
Cyclistic is a (fictional) bike-share company in Chicago. In order to maximize the number of annual memberships, the team wants to understand the difference between casual riders (also referred to as "casual") and annual members (also referred to as "member").

## <a name="toc" />Table of Contents
[A. Data Sources](#ptA)</br>
[B. Cleaning Documentation](#ptB)</br>
Summary of Analysis
Supporting Visualizations
Recommendations

## <a name="ptA" />A. Data Sources
The data is downloaded from <a href="https://divvy-tripdata.s3.amazonaws.com/index.html">this website</a> as zip files. The data has been provided according to the Divvy Data License Agreement. You can read more on <a href="https://divvybikes.com/system-data">their website</a>.

For this report, I have chosen to look at a complete year of data. As of this writing this report, the latest full year of data is from 2022. The 

The raw data for each month in 2022 was downloaded and placed in a folder labeled "Raw Data" in the project main folder.

[Jump to Top](#toc)<br/>

## <a name="ptB"/>B. Cleaning Documentation
After downloading the zip files, I unzipped the csv files and copied them to a new folder labeled CSV. I further copied these files to a file labeled "Prepared Data" to prepare them processing.

Given the sizes of some of these files, spreadsheets was ruled out to handle the data as the June, July, and August reports were unable to be opened. However, they were processed in excel and then R.

For all 12 CSVs, the following process was conducted:

1. The file was opened in Excel.
2. Columns I, J, K, and L were removed. These columns were determined to not be relevant to this business task.
3. A new column J was labeled "length_of_trip"
4. J2 was filled with "=D2-C2" to get the length of the trip. This was then applied to all rows.
5. A new column K was labeled "day_of_week"
6. K2 was filled with "=WEEKDAY(C2,1)" to get the day the trip started. The "1" signifies that the numbering starts on "Sunday" with "1" and ends with "Saturday" with "7". This was then applied to all rows.
7. Column K was then Formatted with the Custom h:mm:ss to get the format to where it was needed for analysis.
8. The sheet was then sorted "smallest to largest" to determine if there were any lengths that were in the negatives. 
9. The rows that had negatives were adjusted by switching their start and end times. Double check that the J column was still "end-start"
10. The sheet was then resorted by "started_at" (column C)
11. Columns J and K were then copied then pasted with just the values.
12. Finally, the CSV was renamed, appending "_Prepped" to the original file name. Example: "202201-divvy0tripdata" became "202201-divvy0tripdata_Prepped"

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
