---
title: "Cyclistic Case Study"
author: "Steve Tamayo"
date: "2023-09-02"
output: html_document
---

```{r setup, include=FALSE}
#rm(list=ls())
knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE)
library(tidyverse)  #helps wrangle data
library(lubridate)  #helps wrangle date attributes
library(ggplot2)  #helps visualize data
library(scales) #helps manage scale of data
library(tidyr)
library(knitr) # for report tables
```

## Introduction

This is a report for the Case Study 1 of the Coursera Google Data Analytics Capstone.

## Business Task Statement

#### "How do annual members and casual riders use Cyclistic bikes differently?"
Cyclistic is a (fictional) bike-share company in Chicago. In order to maximize the number of annual memberships, the team wants to understand the difference between casual riders (also referred to as "casual") and annual members (also referred to as "member").

## <a name="toc" />Table of Contents
[A. Data Sources](#ptA)</br>
[B. Cleaning Documentation](#ptB)</br>
[C. Analysis](#ptC)</br>
[D. Supporting Visualizations](#ptD)</br>
[E. Recommendations](#ptE)</br>
[F. Appendix](#ptF)</br>

## <a name="ptA" />A. Data Sources
The data is downloaded from <a href="https://divvy-tripdata.s3.amazonaws.com/index.html">this website</a> as zip files. The data has been provided according to the Divvy Data License Agreement. You can read more on <a href="https://divvybikes.com/system-data">their website</a>.

For this report, I have chosen to look at a complete year of data. As of this writing this report, the latest full year of data is from 2022. The 

The raw data for each month in 2022 was downloaded and placed in a folder labeled "Raw Data" in the project main folder.

[Jump to Top](#toc)<br/>

## <a name="ptB"/>B. Cleaning Documentation
### Excel Cleaning
After downloading the zip files, I unzipped the csv files and copied them to a new folder labeled CSV. I further copied these files to a file labeled "Prepared Data" to prepare them processing.

Given the sizes of some of these files, spreadsheets was ruled out to handle the data as the June, July, and August reports were unable to be opened. However, they were processed in excel and then R.

For all 12 CSVs, the following process was conducted:

1. The file was opened in Excel.
2. Columns I, J, K, and L were removed. These columns were determined to not be relevant to this business task.
3. A new column J was labeled "length_of_trip"
4. J2 was filled with "=D2-C2" to get the length of the trip. This was then applied to all rows.
5. A new column K was labeled "day_of_week"
6. K2 was filled with "=WEEKDAY(C2,1)" to get the day the trip started. The "1" signifies that the numbering starts on "Sunday" with "1" and ends with "Saturday" with "7". This was then applied to all rows.
7. Column K was then Formatted with the Custom h:mm:ss to get the format to where it was needed for analysis.
8. The sheet was then sorted "smallest to largest" to determine if there were any lengths that were in the negatives. 
9. The rows that had negatives were adjusted by switching their start and end times. Double check that the J column was still "end-start"
10. The sheet was then resorted by "started_at" (column C)
11. Columns J and K were then copied then pasted with just the values.
12. Finally, the CSV was renamed, appending "_Prepped" to the original file name. Example: "202201-divvy0tripdata" became "202201-divvy0tripdata_Prepped"

Following those 12 steps for the 12 CSVs, I loaded them into a new RStudio project.

```{r Load CSVs, include=TRUE}
jan_2022 <- read_csv("202201-divvy-tripdata_Prepped.csv")
feb_2022 <- read_csv("202202-divvy-tripdata_Prepped.csv")
mar_2022 <- read_csv("202203-divvy-tripdata_Prepped.csv")
apr_2022 <- read_csv("202204-divvy-tripdata_Prepped.csv")
may_2022 <- read_csv("202205-divvy-tripdata_Prepped.csv")
jun_2022 <- read_csv("202206-divvy-tripdata_Prepped.csv")
jul_2022 <- read_csv("202207-divvy-tripdata_Prepped.csv")
aug_2022 <- read_csv("202208-divvy-tripdata_Prepped.csv")
sep_2022 <- read_csv("202209-divvy-tripdata_Prepped.csv")
oct_2022 <- read_csv("202210-divvy-tripdata_Prepped.csv")
nov_2022 <- read_csv("202211-divvy-tripdata_Prepped.csv")
dec_2022 <- read_csv("202212-divvy-tripdata_Prepped.csv")
```


### R Cleaning

Upon loading the CSVs into R Studio, I came across a problem. Certain values of "length_of_trip" were being converted to N/A's. Investigating revealed that these values were not converting into the ISO8601 date format R was expecting. Looking further into the CSVs in Excel, these trip lengths were over a week long and therefore were determined to be outliers. Additionally there were a number of trips that had 0 length. I conducted additional cleaning in R by creating the following function:

```{r Function remove_outliers}
## Removes N/A, Trips with 0 length, and assigns the length of trip to a format accepted in R
remove_outliers = function(input_dataframe){
  tmp_df <- drop_na(input_dataframe,length_of_trip)
  tmp_df2 <- cbind(tmp_df,length_of_trip_r = as.POSIXct(tmp_df$length_of_trip,format="%H:%M:%S"))
  return <- subset(tmp_df2,length_of_trip_r > 0)
}
```

This function was then applied to each loaded file and assigned a new variable.

```{r Clean Prepared Excel Data}
jan_2022_clean <- remove_outliers(jan_2022)
feb_2022_clean <- remove_outliers(feb_2022)
mar_2022_clean <- remove_outliers(mar_2022)
apr_2022_clean <- remove_outliers(apr_2022)
may_2022_clean <- remove_outliers(may_2022)
jun_2022_clean <- remove_outliers(jun_2022)
jul_2022_clean <- remove_outliers(jul_2022)
aug_2022_clean <- remove_outliers(aug_2022)
sep_2022_clean <- remove_outliers(sep_2022)
oct_2022_clean <- remove_outliers(oct_2022)
nov_2022_clean <- remove_outliers(nov_2022)
dec_2022_clean <- remove_outliers(dec_2022)
```

## <a name="ptC"/>C. Analysis
<a name="Ref1" />
Now that the data is cleaned, it was time to aggregate the data into something more manageable. I created several functions to help with this process. The full code can be found in the [Appendix here](#Appx1).

```{r Analysis Functions, include=FALSE}

# Function - Filters member status and day of the week
filter_mc_dow = function(input_cleandata,input_MC,input_dow){
  return <- subset(select(input_cleandata, ride_id,rideable_type,length_of_trip,day_of_week,member_casual,length_of_trip_r),
                   member_casual==input_MC & day_of_week==input_dow)
}

# Function - Handle Quantile data
## Get all Quantile data and put it into a dataframe
create_df_q_data <- function(input_cleandata,input_MC){
  
  # Get quantile for each day
  tmp_quantile_1 <- quantile(filter_mc_dow(input_cleandata,input_MC,1)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_2 <- quantile(filter_mc_dow(input_cleandata,input_MC,2)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_3 <- quantile(filter_mc_dow(input_cleandata,input_MC,3)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_4 <- quantile(filter_mc_dow(input_cleandata,input_MC,4)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_5 <- quantile(filter_mc_dow(input_cleandata,input_MC,5)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_6 <- quantile(filter_mc_dow(input_cleandata,input_MC,6)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_7 <- quantile(filter_mc_dow(input_cleandata,input_MC,7)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  
  return <- data.frame(day_of_week = c("Sun","Mon","Tues","Wed","Thurs","Fri","Sat"),
                       day_of_week_num = c(rep(1:7,3)),
                       Q1 = c(
                         tmp_quantile_1[2],
                         tmp_quantile_2[2],
                         tmp_quantile_3[2],
                         tmp_quantile_4[2],
                         tmp_quantile_5[2],
                         tmp_quantile_6[2],
                         tmp_quantile_7[2]
                       ),
                       Q2 = c(
                         tmp_quantile_1[3],
                         tmp_quantile_2[3],
                         tmp_quantile_3[3],
                         tmp_quantile_4[3],
                         tmp_quantile_5[3],
                         tmp_quantile_6[3],
                         tmp_quantile_7[3]
                       ),
                       Q3 = c(
                         tmp_quantile_1[4],
                         tmp_quantile_2[4],
                         tmp_quantile_3[4],
                         tmp_quantile_4[4],
                         tmp_quantile_5[4],
                         tmp_quantile_6[4],
                         tmp_quantile_7[4]
                       ),
                       Q4 = c(
                         tmp_quantile_1[5],
                         tmp_quantile_2[5],
                         tmp_quantile_3[5],
                         tmp_quantile_4[5],
                         tmp_quantile_5[5],
                         tmp_quantile_6[5],
                         tmp_quantile_7[5]
                       )
                       )
}

# Function - Create table of number of trips
create_df_num_of_trips <- function(input_cleandata,input_MorC){
  return <- data.frame(day_of_week = c("Sun","Mon","Tues","Wed","Thurs","Fri","Sat"),
                       num_of_trips = c(nrow(filter_mc_dow(input_cleandata,input_MorC,1)),
                                        nrow(filter_mc_dow(input_cleandata,input_MorC,2)),
                                        nrow(filter_mc_dow(input_cleandata,input_MorC,3)),
                                        nrow(filter_mc_dow(input_cleandata,input_MorC,4)),
                                        nrow(filter_mc_dow(input_cleandata,input_MorC,5)),
                                        nrow(filter_mc_dow(input_cleandata,input_MorC,6)),
                                        nrow(filter_mc_dow(input_cleandata,input_MorC,7))
                       )
  )
}
# Function - Create a table of number of trips that less than Q2
create_df_num_of_trips_q <- function(input_cleandata,input_MorC,input_q){
  
  
  tmp_filter_data_MorC1 <-filter_mc_dow(input_cleandata,input_MorC,1)
  tmp_filter_data_MorC2 <-filter_mc_dow(input_cleandata,input_MorC,2)
  tmp_filter_data_MorC3 <-filter_mc_dow(input_cleandata,input_MorC,3)
  tmp_filter_data_MorC4 <-filter_mc_dow(input_cleandata,input_MorC,4)
  tmp_filter_data_MorC5 <-filter_mc_dow(input_cleandata,input_MorC,5)
  tmp_filter_data_MorC6 <-filter_mc_dow(input_cleandata,input_MorC,6)
  tmp_filter_data_MorC7 <-filter_mc_dow(input_cleandata,input_MorC,7)
  
  # Get quantile for each day
  tmp_quantile_1 <- quantile(filter_mc_dow(input_cleandata,input_MorC,1)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_2 <- quantile(filter_mc_dow(input_cleandata,input_MorC,2)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_3 <- quantile(filter_mc_dow(input_cleandata,input_MorC,3)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_4 <- quantile(filter_mc_dow(input_cleandata,input_MorC,4)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_5 <- quantile(filter_mc_dow(input_cleandata,input_MorC,5)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_6 <- quantile(filter_mc_dow(input_cleandata,input_MorC,6)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_7 <- quantile(filter_mc_dow(input_cleandata,input_MorC,7)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  
  
  return <- data.frame(day_of_week = c("Sun","Mon","Tues","Wed","Thurs","Fri","Sat"),
                       num_of_trips = c(sum(tmp_filter_data_MorC1$length_of_trip_r <= tmp_quantile_1[input_q]),
                                        sum(tmp_filter_data_MorC2$length_of_trip_r <= tmp_quantile_2[input_q]),
                                        sum(tmp_filter_data_MorC3$length_of_trip_r <= tmp_quantile_3[input_q]),
                                        sum(tmp_filter_data_MorC4$length_of_trip_r <= tmp_quantile_4[input_q]),
                                        sum(tmp_filter_data_MorC5$length_of_trip_r <= tmp_quantile_5[input_q]),
                                        sum(tmp_filter_data_MorC6$length_of_trip_r <= tmp_quantile_6[input_q]),
                                        sum(tmp_filter_data_MorC7$length_of_trip_r <= tmp_quantile_7[input_q])
                                        )
                      )
}

# Function - Find Num of Bikes Used per day per type of user
## Writing a function to make finding bike values cleaner
find_bike_data <- function(input_clean_data_rideable_type,input_clean_data_member_casual,memberOrCasual,input_clean_data_day_of_week){
  return <- data.frame(day_of_week = c("Sun","Mon","Tues","Wed","Thurs","Fri","Sat"),
                       classic_bike = c(sum(input_clean_data_rideable_type == "classic_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 1),
                                        sum(input_clean_data_rideable_type == "classic_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 2),
                                        sum(input_clean_data_rideable_type == "classic_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 3),
                                        sum(input_clean_data_rideable_type == "classic_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 4),
                                        sum(input_clean_data_rideable_type == "classic_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 5),
                                        sum(input_clean_data_rideable_type == "classic_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 6),
                                        sum(input_clean_data_rideable_type == "classic_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 7)
                                        ),
                       docked_bike = c(sum(input_clean_data_rideable_type == "docked_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 1),
                                       sum(input_clean_data_rideable_type == "docked_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 2),
                                       sum(input_clean_data_rideable_type == "docked_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 3),
                                       sum(input_clean_data_rideable_type == "docked_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 4),
                                       sum(input_clean_data_rideable_type == "docked_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 5),
                                       sum(input_clean_data_rideable_type == "docked_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 6),
                                       sum(input_clean_data_rideable_type == "docked_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 7)
                                       ),
                       electric_bike = c(sum(input_clean_data_rideable_type == "electric_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 1),
                                         sum(input_clean_data_rideable_type == "electric_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 2),
                                         sum(input_clean_data_rideable_type == "electric_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 3),
                                         sum(input_clean_data_rideable_type == "electric_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 4),
                                         sum(input_clean_data_rideable_type == "electric_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 5),
                                         sum(input_clean_data_rideable_type == "electric_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 6),
                                         sum(input_clean_data_rideable_type == "electric_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 7)
                                       ),
                       total = c(sum(input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 1),
                                      sum(input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 2),
                                      sum(input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 3),
                                      sum(input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 4),
                                      sum(input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 5),
                                      sum(input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 6),
                                      sum(input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 7)
                                      )
  )
}
```
<a name="Ref2" />
These functions were then able to be applied to all of the clean data. Code is include in the [Appendix here](#Appx2).
```{r Applying Functions to Clean Data, include=FALSE}
# JANUARY
jan_2022_casual_df <- create_df_num_of_trips(jan_2022_clean,"casual")
jan_2022_member_df <- create_df_num_of_trips(jan_2022_clean,"member")
jan_2022_qAll_casual_df <- create_df_q_data(jan_2022_clean,"casual")
jan_2022_qAll_member_df <- create_df_q_data(jan_2022_clean,"member")
jan_2022_q2_casual_df <- create_df_num_of_trips_q(jan_2022_clean,"casual",3)
jan_2022_q2_member_df <- create_df_num_of_trips_q(jan_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
jan_2022_bike_type_Casual_df <- find_bike_data(jan_2022_clean$rideable_type,jan_2022_clean$member_casual,"casual",jan_2022_clean$day_of_week)
jan_2022_bike_type_Member_df <- find_bike_data(jan_2022_clean$rideable_type,jan_2022_clean$member_casual,"member",jan_2022_clean$day_of_week)

# FEBRUARY
feb_2022_casual_df <- create_df_num_of_trips(feb_2022_clean,"casual")
feb_2022_member_df <- create_df_num_of_trips(feb_2022_clean,"member")
feb_2022_qAll_casual_df <- create_df_q_data(feb_2022_clean,"casual")
feb_2022_qAll_member_df <- create_df_q_data(feb_2022_clean,"member")
feb_2022_q2_casual_df <- create_df_num_of_trips_q(feb_2022_clean,"casual",3)
feb_2022_q2_member_df <- create_df_num_of_trips_q(feb_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
feb_2022_bike_type_Casual_df <- find_bike_data(feb_2022_clean$rideable_type,feb_2022_clean$member_casual,"casual",feb_2022_clean$day_of_week)
feb_2022_bike_type_Member_df <- find_bike_data(feb_2022_clean$rideable_type,feb_2022_clean$member_casual,"member",feb_2022_clean$day_of_week)


# MARCH
mar_2022_casual_df <- create_df_num_of_trips(mar_2022_clean,"casual")
mar_2022_member_df <- create_df_num_of_trips(mar_2022_clean,"member")
mar_2022_qAll_casual_df <- create_df_q_data(mar_2022_clean,"casual")
mar_2022_qAll_member_df <- create_df_q_data(mar_2022_clean,"member")
mar_2022_q2_casual_df <- create_df_num_of_trips_q(mar_2022_clean,"casual",3)
mar_2022_q2_member_df <- create_df_num_of_trips_q(mar_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
mar_2022_bike_type_Casual_df <- find_bike_data(mar_2022_clean$rideable_type,mar_2022_clean$member_casual,"casual",mar_2022_clean$day_of_week)
mar_2022_bike_type_Member_df <- find_bike_data(mar_2022_clean$rideable_type,mar_2022_clean$member_casual,"member",mar_2022_clean$day_of_week)

# APRIL
apr_2022_casual_df <- create_df_num_of_trips(apr_2022_clean,"casual")
apr_2022_member_df <- create_df_num_of_trips(apr_2022_clean,"member")
apr_2022_qAll_casual_df <- create_df_q_data(apr_2022_clean,"casual")
apr_2022_qAll_member_df <- create_df_q_data(apr_2022_clean,"member")
apr_2022_q2_casual_df <- create_df_num_of_trips_q(apr_2022_clean,"casual",3)
apr_2022_q2_member_df <- create_df_num_of_trips_q(apr_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
apr_2022_bike_type_Casual_df <- find_bike_data(apr_2022_clean$rideable_type,apr_2022_clean$member_casual,"casual",apr_2022_clean$day_of_week)
apr_2022_bike_type_Member_df <- find_bike_data(apr_2022_clean$rideable_type,apr_2022_clean$member_casual,"member",apr_2022_clean$day_of_week)


# MAY
may_2022_casual_df <- create_df_num_of_trips(may_2022_clean,"casual")
may_2022_member_df <- create_df_num_of_trips(may_2022_clean,"member")
may_2022_qAll_casual_df <- create_df_q_data(may_2022_clean,"casual")
may_2022_qAll_member_df <- create_df_q_data(may_2022_clean,"member")
may_2022_q2_casual_df <- create_df_num_of_trips_q(may_2022_clean,"casual",3)
may_2022_q2_member_df <- create_df_num_of_trips_q(may_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
may_2022_bike_type_Casual_df <- find_bike_data(may_2022_clean$rideable_type,may_2022_clean$member_casual,"casual",may_2022_clean$day_of_week)
may_2022_bike_type_Member_df <- find_bike_data(may_2022_clean$rideable_type,may_2022_clean$member_casual,"member",may_2022_clean$day_of_week)


# JUNE
jun_2022_casual_df <- create_df_num_of_trips(jun_2022_clean,"casual")
jun_2022_member_df <- create_df_num_of_trips(jun_2022_clean,"member")
jun_2022_qAll_casual_df <- create_df_q_data(jun_2022_clean,"casual")
jun_2022_qAll_member_df <- create_df_q_data(jun_2022_clean,"member")
jun_2022_q2_casual_df <- create_df_num_of_trips_q(jun_2022_clean,"casual",3)
jun_2022_q2_member_df <- create_df_num_of_trips_q(jun_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
jun_2022_bike_type_Casual_df <- find_bike_data(jun_2022_clean$rideable_type,jun_2022_clean$member_casual,"casual",jun_2022_clean$day_of_week)
jun_2022_bike_type_Member_df <- find_bike_data(jun_2022_clean$rideable_type,jun_2022_clean$member_casual,"member",jun_2022_clean$day_of_week)


# JULY
jul_2022_casual_df <- create_df_num_of_trips(jul_2022_clean,"casual")
jul_2022_member_df <- create_df_num_of_trips(jul_2022_clean,"member")
jul_2022_qAll_casual_df <- create_df_q_data(jul_2022_clean,"casual")
jul_2022_qAll_member_df <- create_df_q_data(jul_2022_clean,"member")
jul_2022_q2_casual_df <- create_df_num_of_trips_q(jul_2022_clean,"casual",3)
jul_2022_q2_member_df <- create_df_num_of_trips_q(jul_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
jul_2022_bike_type_Casual_df <- find_bike_data(jul_2022_clean$rideable_type,jul_2022_clean$member_casual,"casual",jul_2022_clean$day_of_week)
jul_2022_bike_type_Member_df <- find_bike_data(jul_2022_clean$rideable_type,jul_2022_clean$member_casual,"member",jul_2022_clean$day_of_week)


# AUGUST
aug_2022_casual_df <- create_df_num_of_trips(aug_2022_clean,"casual")
aug_2022_member_df <- create_df_num_of_trips(aug_2022_clean,"member")
aug_2022_qAll_casual_df <- create_df_q_data(aug_2022_clean,"casual")
aug_2022_qAll_member_df <- create_df_q_data(aug_2022_clean,"member")
aug_2022_q2_casual_df <- create_df_num_of_trips_q(aug_2022_clean,"casual",3)
aug_2022_q2_member_df <- create_df_num_of_trips_q(aug_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
aug_2022_bike_type_Casual_df <- find_bike_data(aug_2022_clean$rideable_type,aug_2022_clean$member_casual,"casual",aug_2022_clean$day_of_week)
aug_2022_bike_type_Member_df <- find_bike_data(aug_2022_clean$rideable_type,aug_2022_clean$member_casual,"member",aug_2022_clean$day_of_week)


# SEPTEMBER
sep_2022_casual_df <- create_df_num_of_trips(sep_2022_clean,"casual")
sep_2022_member_df <- create_df_num_of_trips(sep_2022_clean,"member")
sep_2022_qAll_casual_df <- create_df_q_data(sep_2022_clean,"casual")
sep_2022_qAll_member_df <- create_df_q_data(sep_2022_clean,"member")
sep_2022_q2_casual_df <- create_df_num_of_trips_q(sep_2022_clean,"casual",3)
sep_2022_q2_member_df <- create_df_num_of_trips_q(sep_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
sep_2022_bike_type_Casual_df <- find_bike_data(sep_2022_clean$rideable_type,sep_2022_clean$member_casual,"casual",sep_2022_clean$day_of_week)
sep_2022_bike_type_Member_df <- find_bike_data(sep_2022_clean$rideable_type,sep_2022_clean$member_casual,"member",sep_2022_clean$day_of_week)


# OCTOBER
oct_2022_casual_df <- create_df_num_of_trips(oct_2022_clean,"casual")
oct_2022_member_df <- create_df_num_of_trips(oct_2022_clean,"member")
oct_2022_qAll_casual_df <- create_df_q_data(oct_2022_clean,"casual")
oct_2022_qAll_member_df <- create_df_q_data(oct_2022_clean,"member")
oct_2022_q2_casual_df <- create_df_num_of_trips_q(oct_2022_clean,"casual",3)
oct_2022_q2_member_df <- create_df_num_of_trips_q(oct_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
oct_2022_bike_type_Casual_df <- find_bike_data(oct_2022_clean$rideable_type,oct_2022_clean$member_casual,"casual",oct_2022_clean$day_of_week)
oct_2022_bike_type_Member_df <- find_bike_data(oct_2022_clean$rideable_type,oct_2022_clean$member_casual,"member",oct_2022_clean$day_of_week)

# NOVEMBER
nov_2022_casual_df <- create_df_num_of_trips(nov_2022_clean,"casual")
nov_2022_member_df <- create_df_num_of_trips(nov_2022_clean,"member")
nov_2022_qAll_casual_df <- create_df_q_data(nov_2022_clean,"casual")
nov_2022_qAll_member_df <- create_df_q_data(nov_2022_clean,"member")
nov_2022_q2_casual_df <- create_df_num_of_trips_q(nov_2022_clean,"casual",3)
nov_2022_q2_member_df <- create_df_num_of_trips_q(nov_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
nov_2022_bike_type_Casual_df <- find_bike_data(nov_2022_clean$rideable_type,nov_2022_clean$member_casual,"casual",nov_2022_clean$day_of_week)
nov_2022_bike_type_Member_df <- find_bike_data(nov_2022_clean$rideable_type,nov_2022_clean$member_casual,"member",nov_2022_clean$day_of_week)

# DECEMBER
dec_2022_casual_df <- create_df_num_of_trips(dec_2022_clean,"casual")
dec_2022_member_df <- create_df_num_of_trips(dec_2022_clean,"member")
dec_2022_qAll_casual_df <- create_df_q_data(dec_2022_clean,"casual")
dec_2022_qAll_member_df <- create_df_q_data(dec_2022_clean,"member")
dec_2022_q2_casual_df <- create_df_num_of_trips_q(dec_2022_clean,"casual",3)
dec_2022_q2_member_df <- create_df_num_of_trips_q(dec_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
dec_2022_bike_type_Casual_df <- find_bike_data(dec_2022_clean$rideable_type,dec_2022_clean$member_casual,"casual",dec_2022_clean$day_of_week)
dec_2022_bike_type_Member_df <- find_bike_data(dec_2022_clean$rideable_type,dec_2022_clean$member_casual,"member",dec_2022_clean$day_of_week)

```

The new tables display the following for each month (Displaying January only):

Number of trips for each month by member status and bike_type (Casual & Member are separate)

##### Casual

```{r Example Number of Trips Jan - Casual, include=FALSE}
kable(jan_2022_bike_type_Casual_df,caption = "Number of Trips Jan - Casual")
```

##### Member

```{r Example Number of Trips Jan - Member, include=FALSE}
kable(jan_2022_bike_type_Member_df,caption = "Number of Trips Jan - Member")
```


## <a name="ptF" />F. Appendix

### Bulky Code:
This section contains code mentioned in the report. Code here will not evaluate.

#### <a name="Appx1"/>Anaylsis Functions
[Jump to report this is used](#Ref1)
```{r APPX: Analysis Functions, include=TRUE, eval=FALSE}

# Function - Filters member status and day of the week
filter_mc_dow = function(input_cleandata,input_MC,input_dow){
  return <- subset(select(input_cleandata, ride_id,rideable_type,length_of_trip,day_of_week,member_casual,length_of_trip_r),
                   member_casual==input_MC & day_of_week==input_dow)
}

# Function - Handle Quantile data
## Get all Quantile data and put it into a dataframe
create_df_q_data <- function(input_cleandata,input_MC){
  
  # Get quantile for each day
  tmp_quantile_1 <- quantile(filter_mc_dow(input_cleandata,input_MC,1)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_2 <- quantile(filter_mc_dow(input_cleandata,input_MC,2)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_3 <- quantile(filter_mc_dow(input_cleandata,input_MC,3)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_4 <- quantile(filter_mc_dow(input_cleandata,input_MC,4)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_5 <- quantile(filter_mc_dow(input_cleandata,input_MC,5)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_6 <- quantile(filter_mc_dow(input_cleandata,input_MC,6)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_7 <- quantile(filter_mc_dow(input_cleandata,input_MC,7)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  
  return <- data.frame(day_of_week = c("Sun","Mon","Tues","Wed","Thurs","Fri","Sat"),
                       day_of_week_num = c(rep(1:7,3)),
                       Q1 = c(
                         tmp_quantile_1[2],
                         tmp_quantile_2[2],
                         tmp_quantile_3[2],
                         tmp_quantile_4[2],
                         tmp_quantile_5[2],
                         tmp_quantile_6[2],
                         tmp_quantile_7[2]
                       ),
                       Q2 = c(
                         tmp_quantile_1[3],
                         tmp_quantile_2[3],
                         tmp_quantile_3[3],
                         tmp_quantile_4[3],
                         tmp_quantile_5[3],
                         tmp_quantile_6[3],
                         tmp_quantile_7[3]
                       ),
                       Q3 = c(
                         tmp_quantile_1[4],
                         tmp_quantile_2[4],
                         tmp_quantile_3[4],
                         tmp_quantile_4[4],
                         tmp_quantile_5[4],
                         tmp_quantile_6[4],
                         tmp_quantile_7[4]
                       ),
                       Q4 = c(
                         tmp_quantile_1[5],
                         tmp_quantile_2[5],
                         tmp_quantile_3[5],
                         tmp_quantile_4[5],
                         tmp_quantile_5[5],
                         tmp_quantile_6[5],
                         tmp_quantile_7[5]
                       )
                       )
}

# Function - Create table of number of trips
create_df_num_of_trips <- function(input_cleandata,input_MorC){
  return <- data.frame(day_of_week = c("Sun","Mon","Tues","Wed","Thurs","Fri","Sat"),
                       num_of_trips = c(nrow(filter_mc_dow(input_cleandata,input_MorC,1)),
                                        nrow(filter_mc_dow(input_cleandata,input_MorC,2)),
                                        nrow(filter_mc_dow(input_cleandata,input_MorC,3)),
                                        nrow(filter_mc_dow(input_cleandata,input_MorC,4)),
                                        nrow(filter_mc_dow(input_cleandata,input_MorC,5)),
                                        nrow(filter_mc_dow(input_cleandata,input_MorC,6)),
                                        nrow(filter_mc_dow(input_cleandata,input_MorC,7))
                       )
  )
}
# Function - Create a table of number of trips that less than Q2
create_df_num_of_trips_q <- function(input_cleandata,input_MorC,input_q){
  
  
  tmp_filter_data_MorC1 <-filter_mc_dow(input_cleandata,input_MorC,1)
  tmp_filter_data_MorC2 <-filter_mc_dow(input_cleandata,input_MorC,2)
  tmp_filter_data_MorC3 <-filter_mc_dow(input_cleandata,input_MorC,3)
  tmp_filter_data_MorC4 <-filter_mc_dow(input_cleandata,input_MorC,4)
  tmp_filter_data_MorC5 <-filter_mc_dow(input_cleandata,input_MorC,5)
  tmp_filter_data_MorC6 <-filter_mc_dow(input_cleandata,input_MorC,6)
  tmp_filter_data_MorC7 <-filter_mc_dow(input_cleandata,input_MorC,7)
  
  # Get quantile for each day
  tmp_quantile_1 <- quantile(filter_mc_dow(input_cleandata,input_MorC,1)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_2 <- quantile(filter_mc_dow(input_cleandata,input_MorC,2)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_3 <- quantile(filter_mc_dow(input_cleandata,input_MorC,3)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_4 <- quantile(filter_mc_dow(input_cleandata,input_MorC,4)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_5 <- quantile(filter_mc_dow(input_cleandata,input_MorC,5)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_6 <- quantile(filter_mc_dow(input_cleandata,input_MorC,6)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  tmp_quantile_7 <- quantile(filter_mc_dow(input_cleandata,input_MorC,7)$length_of_trip_r,probs = c(0,0.25,0.5,0.75,1)) 
  
  
  return <- data.frame(day_of_week = c("Sun","Mon","Tues","Wed","Thurs","Fri","Sat"),
                       num_of_trips = c(sum(tmp_filter_data_MorC1$length_of_trip_r <= tmp_quantile_1[input_q]),
                                        sum(tmp_filter_data_MorC2$length_of_trip_r <= tmp_quantile_2[input_q]),
                                        sum(tmp_filter_data_MorC3$length_of_trip_r <= tmp_quantile_3[input_q]),
                                        sum(tmp_filter_data_MorC4$length_of_trip_r <= tmp_quantile_4[input_q]),
                                        sum(tmp_filter_data_MorC5$length_of_trip_r <= tmp_quantile_5[input_q]),
                                        sum(tmp_filter_data_MorC6$length_of_trip_r <= tmp_quantile_6[input_q]),
                                        sum(tmp_filter_data_MorC7$length_of_trip_r <= tmp_quantile_7[input_q])
                                        )
                      )
}

# Function - Find Num of Bikes Used per day per type of user
## Writing a function to make finding bike values cleaner
find_bike_data <- function(input_clean_data_rideable_type,input_clean_data_member_casual,memberOrCasual,input_clean_data_day_of_week){
  return <- data.frame(day_of_week = c("Sun","Mon","Tues","Wed","Thurs","Fri","Sat"),
                       classic_bike = c(sum(input_clean_data_rideable_type == "classic_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 1),
                                        sum(input_clean_data_rideable_type == "classic_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 2),
                                        sum(input_clean_data_rideable_type == "classic_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 3),
                                        sum(input_clean_data_rideable_type == "classic_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 4),
                                        sum(input_clean_data_rideable_type == "classic_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 5),
                                        sum(input_clean_data_rideable_type == "classic_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 6),
                                        sum(input_clean_data_rideable_type == "classic_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 7)
                                        ),
                       docked_bike = c(sum(input_clean_data_rideable_type == "docked_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 1),
                                       sum(input_clean_data_rideable_type == "docked_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 2),
                                       sum(input_clean_data_rideable_type == "docked_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 3),
                                       sum(input_clean_data_rideable_type == "docked_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 4),
                                       sum(input_clean_data_rideable_type == "docked_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 5),
                                       sum(input_clean_data_rideable_type == "docked_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 6),
                                       sum(input_clean_data_rideable_type == "docked_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 7)
                                       ),
                       electric_bike = c(sum(input_clean_data_rideable_type == "electric_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 1),
                                         sum(input_clean_data_rideable_type == "electric_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 2),
                                         sum(input_clean_data_rideable_type == "electric_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 3),
                                         sum(input_clean_data_rideable_type == "electric_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 4),
                                         sum(input_clean_data_rideable_type == "electric_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 5),
                                         sum(input_clean_data_rideable_type == "electric_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 6),
                                         sum(input_clean_data_rideable_type == "electric_bike" & input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 7)
                                       ),
                       total = c(sum(input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 1),
                                      sum(input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 2),
                                      sum(input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 3),
                                      sum(input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 4),
                                      sum(input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 5),
                                      sum(input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 6),
                                      sum(input_clean_data_member_casual==memberOrCasual& input_clean_data_day_of_week == 7)
                                      )
  )
}
```

#### <a name="Appx2"/>Applying Functions to Clean Data
[Jump to report this is used](#Ref2)
```{r APPX: Applying Functions to Clean Data, include=TRUE, eval=FALSE}
# JANUARY
jan_2022_casual_df <- create_df_num_of_trips(jan_2022_clean,"casual")
jan_2022_member_df <- create_df_num_of_trips(jan_2022_clean,"member")
jan_2022_qAll_casual_df <- create_df_q_data(jan_2022_clean,"casual")
jan_2022_qAll_member_df <- create_df_q_data(jan_2022_clean,"member")
jan_2022_q2_casual_df <- create_df_num_of_trips_q(jan_2022_clean,"casual",3)
jan_2022_q2_member_df <- create_df_num_of_trips_q(jan_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
jan_2022_bike_type_Casual_df <- find_bike_data(jan_2022_clean$rideable_type,jan_2022_clean$member_casual,"casual",jan_2022_clean$day_of_week)
jan_2022_bike_type_Member_df <- find_bike_data(jan_2022_clean$rideable_type,jan_2022_clean$member_casual,"member",jan_2022_clean$day_of_week)

# FEBRUARY
feb_2022_casual_df <- create_df_num_of_trips(feb_2022_clean,"casual")
feb_2022_member_df <- create_df_num_of_trips(feb_2022_clean,"member")
feb_2022_qAll_casual_df <- create_df_q_data(feb_2022_clean,"casual")
feb_2022_qAll_member_df <- create_df_q_data(feb_2022_clean,"member")
feb_2022_q2_casual_df <- create_df_num_of_trips_q(feb_2022_clean,"casual",3)
feb_2022_q2_member_df <- create_df_num_of_trips_q(feb_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
feb_2022_bike_type_Casual_df <- find_bike_data(feb_2022_clean$rideable_type,feb_2022_clean$member_casual,"casual",feb_2022_clean$day_of_week)
feb_2022_bike_type_Member_df <- find_bike_data(feb_2022_clean$rideable_type,feb_2022_clean$member_casual,"member",feb_2022_clean$day_of_week)


# MARCH
mar_2022_casual_df <- create_df_num_of_trips(mar_2022_clean,"casual")
mar_2022_member_df <- create_df_num_of_trips(mar_2022_clean,"member")
mar_2022_qAll_casual_df <- create_df_q_data(mar_2022_clean,"casual")
mar_2022_qAll_member_df <- create_df_q_data(mar_2022_clean,"member")
mar_2022_q2_casual_df <- create_df_num_of_trips_q(mar_2022_clean,"casual",3)
mar_2022_q2_member_df <- create_df_num_of_trips_q(mar_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
mar_2022_bike_type_Casual_df <- find_bike_data(mar_2022_clean$rideable_type,mar_2022_clean$member_casual,"casual",mar_2022_clean$day_of_week)
mar_2022_bike_type_Member_df <- find_bike_data(mar_2022_clean$rideable_type,mar_2022_clean$member_casual,"member",mar_2022_clean$day_of_week)

# APRIL
apr_2022_casual_df <- create_df_num_of_trips(apr_2022_clean,"casual")
apr_2022_member_df <- create_df_num_of_trips(apr_2022_clean,"member")
apr_2022_qAll_casual_df <- create_df_q_data(apr_2022_clean,"casual")
apr_2022_qAll_member_df <- create_df_q_data(apr_2022_clean,"member")
apr_2022_q2_casual_df <- create_df_num_of_trips_q(apr_2022_clean,"casual",3)
apr_2022_q2_member_df <- create_df_num_of_trips_q(apr_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
apr_2022_bike_type_Casual_df <- find_bike_data(apr_2022_clean$rideable_type,apr_2022_clean$member_casual,"casual",apr_2022_clean$day_of_week)
apr_2022_bike_type_Member_df <- find_bike_data(apr_2022_clean$rideable_type,apr_2022_clean$member_casual,"member",apr_2022_clean$day_of_week)


# MAY
may_2022_casual_df <- create_df_num_of_trips(may_2022_clean,"casual")
may_2022_member_df <- create_df_num_of_trips(may_2022_clean,"member")
may_2022_qAll_casual_df <- create_df_q_data(may_2022_clean,"casual")
may_2022_qAll_member_df <- create_df_q_data(may_2022_clean,"member")
may_2022_q2_casual_df <- create_df_num_of_trips_q(may_2022_clean,"casual",3)
may_2022_q2_member_df <- create_df_num_of_trips_q(may_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
may_2022_bike_type_Casual_df <- find_bike_data(may_2022_clean$rideable_type,may_2022_clean$member_casual,"casual",may_2022_clean$day_of_week)
may_2022_bike_type_Member_df <- find_bike_data(may_2022_clean$rideable_type,may_2022_clean$member_casual,"member",may_2022_clean$day_of_week)


# JUNE
jun_2022_casual_df <- create_df_num_of_trips(jun_2022_clean,"casual")
jun_2022_member_df <- create_df_num_of_trips(jun_2022_clean,"member")
jun_2022_qAll_casual_df <- create_df_q_data(jun_2022_clean,"casual")
jun_2022_qAll_member_df <- create_df_q_data(jun_2022_clean,"member")
jun_2022_q2_casual_df <- create_df_num_of_trips_q(jun_2022_clean,"casual",3)
jun_2022_q2_member_df <- create_df_num_of_trips_q(jun_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
jun_2022_bike_type_Casual_df <- find_bike_data(jun_2022_clean$rideable_type,jun_2022_clean$member_casual,"casual",jun_2022_clean$day_of_week)
jun_2022_bike_type_Member_df <- find_bike_data(jun_2022_clean$rideable_type,jun_2022_clean$member_casual,"member",jun_2022_clean$day_of_week)


# JULY
jul_2022_casual_df <- create_df_num_of_trips(jul_2022_clean,"casual")
jul_2022_member_df <- create_df_num_of_trips(jul_2022_clean,"member")
jul_2022_qAll_casual_df <- create_df_q_data(jul_2022_clean,"casual")
jul_2022_qAll_member_df <- create_df_q_data(jul_2022_clean,"member")
jul_2022_q2_casual_df <- create_df_num_of_trips_q(jul_2022_clean,"casual",3)
jul_2022_q2_member_df <- create_df_num_of_trips_q(jul_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
jul_2022_bike_type_Casual_df <- find_bike_data(jul_2022_clean$rideable_type,jul_2022_clean$member_casual,"casual",jul_2022_clean$day_of_week)
jul_2022_bike_type_Member_df <- find_bike_data(jul_2022_clean$rideable_type,jul_2022_clean$member_casual,"member",jul_2022_clean$day_of_week)


# AUGUST
aug_2022_casual_df <- create_df_num_of_trips(aug_2022_clean,"casual")
aug_2022_member_df <- create_df_num_of_trips(aug_2022_clean,"member")
aug_2022_qAll_casual_df <- create_df_q_data(aug_2022_clean,"casual")
aug_2022_qAll_member_df <- create_df_q_data(aug_2022_clean,"member")
aug_2022_q2_casual_df <- create_df_num_of_trips_q(aug_2022_clean,"casual",3)
aug_2022_q2_member_df <- create_df_num_of_trips_q(aug_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
aug_2022_bike_type_Casual_df <- find_bike_data(aug_2022_clean$rideable_type,aug_2022_clean$member_casual,"casual",aug_2022_clean$day_of_week)
aug_2022_bike_type_Member_df <- find_bike_data(aug_2022_clean$rideable_type,aug_2022_clean$member_casual,"member",aug_2022_clean$day_of_week)


# SEPTEMBER
sep_2022_casual_df <- create_df_num_of_trips(sep_2022_clean,"casual")
sep_2022_member_df <- create_df_num_of_trips(sep_2022_clean,"member")
sep_2022_qAll_casual_df <- create_df_q_data(sep_2022_clean,"casual")
sep_2022_qAll_member_df <- create_df_q_data(sep_2022_clean,"member")
sep_2022_q2_casual_df <- create_df_num_of_trips_q(sep_2022_clean,"casual",3)
sep_2022_q2_member_df <- create_df_num_of_trips_q(sep_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
sep_2022_bike_type_Casual_df <- find_bike_data(sep_2022_clean$rideable_type,sep_2022_clean$member_casual,"casual",sep_2022_clean$day_of_week)
sep_2022_bike_type_Member_df <- find_bike_data(sep_2022_clean$rideable_type,sep_2022_clean$member_casual,"member",sep_2022_clean$day_of_week)


# OCTOBER
oct_2022_casual_df <- create_df_num_of_trips(oct_2022_clean,"casual")
oct_2022_member_df <- create_df_num_of_trips(oct_2022_clean,"member")
oct_2022_qAll_casual_df <- create_df_q_data(oct_2022_clean,"casual")
oct_2022_qAll_member_df <- create_df_q_data(oct_2022_clean,"member")
oct_2022_q2_casual_df <- create_df_num_of_trips_q(oct_2022_clean,"casual",3)
oct_2022_q2_member_df <- create_df_num_of_trips_q(oct_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
oct_2022_bike_type_Casual_df <- find_bike_data(oct_2022_clean$rideable_type,oct_2022_clean$member_casual,"casual",oct_2022_clean$day_of_week)
oct_2022_bike_type_Member_df <- find_bike_data(oct_2022_clean$rideable_type,oct_2022_clean$member_casual,"member",oct_2022_clean$day_of_week)

# NOVEMBER
nov_2022_casual_df <- create_df_num_of_trips(nov_2022_clean,"casual")
nov_2022_member_df <- create_df_num_of_trips(nov_2022_clean,"member")
nov_2022_qAll_casual_df <- create_df_q_data(nov_2022_clean,"casual")
nov_2022_qAll_member_df <- create_df_q_data(nov_2022_clean,"member")
nov_2022_q2_casual_df <- create_df_num_of_trips_q(nov_2022_clean,"casual",3)
nov_2022_q2_member_df <- create_df_num_of_trips_q(nov_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
nov_2022_bike_type_Casual_df <- find_bike_data(nov_2022_clean$rideable_type,nov_2022_clean$member_casual,"casual",nov_2022_clean$day_of_week)
nov_2022_bike_type_Member_df <- find_bike_data(nov_2022_clean$rideable_type,nov_2022_clean$member_casual,"member",nov_2022_clean$day_of_week)

# DECEMBER
dec_2022_casual_df <- create_df_num_of_trips(dec_2022_clean,"casual")
dec_2022_member_df <- create_df_num_of_trips(dec_2022_clean,"member")
dec_2022_qAll_casual_df <- create_df_q_data(dec_2022_clean,"casual")
dec_2022_qAll_member_df <- create_df_q_data(dec_2022_clean,"member")
dec_2022_q2_casual_df <- create_df_num_of_trips_q(dec_2022_clean,"casual",3)
dec_2022_q2_member_df <- create_df_num_of_trips_q(dec_2022_clean,"member",3)
# Determining Most Popular Type of Bike
# classic_bike, docked_bike, electric_bike
dec_2022_bike_type_Casual_df <- find_bike_data(dec_2022_clean$rideable_type,dec_2022_clean$member_casual,"casual",dec_2022_clean$day_of_week)
dec_2022_bike_type_Member_df <- find_bike_data(dec_2022_clean$rideable_type,dec_2022_clean$member_casual,"member",dec_2022_clean$day_of_week)

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
